StarCraft Bots and Competitions

### 2015-12-11 ECGG_StarCraftCompetitions/ECGG_StarCraftCompetitions.tex
updated CIG competitions text

\institute{
	Computing Science Department of the University of Alberta, Edmonton, Canada. \\
	\email{cdavid@cs.ualberta.ca}
\and
	Department of Computer Science of Technische Universit{\"a}t Dortmund, Germany.
	\email{mike.preuss@cs.tu-dortmund.de}
\and
	Nantes Atlantic Computer Science Laboratory (LINA) of the Universit{\'e} de Nantes, France. \\
	\email{florian.richoux@univ-nantes.fr}
\and
	Cognitive Science and Psycholinguistics (LSCP) of ENS Ulm, Paris, France. \\
	\email{gabriel.synnaeve@gmail.com}
\and
	Computer Science Department at Drexel University, Philadelphia, PA, USA. \\
	\email{\{santi,albertouri\}@cs.drexel.edu}
}

@@

\subsubsection{CIG 2013}

Mike will fill this out?

>>>>

\institute{
	Computing Science Department of the University of Alberta, Edmonton, Canada. \\
	\email{cdavid@cs.ualberta.ca}
\and
	Information Systems and Statistics, Westf. Wilhelmsuniversit{\"a}t M{\"u}nster, Germany.
	\email{mike.preuss@uni-muenster.de}
\and
	Nantes Atlantic Computer Science Laboratory (LINA) of the Universit{\'e} de Nantes, France. \\
	\email{florian.richoux@univ-nantes.fr}
\and
	Cognitive Science and Psycholinguistics (LSCP) of ENS Ulm, Paris, France. \\
	\email{gabriel.synnaeve@gmail.com}
\and
	Computer Science Department at Drexel University, Philadelphia, PA, USA. \\
	\email{\{santi,albertouri\}@cs.drexel.edu}
}

@@

\subsubsection{CIG 2013} The CIG 2013 competition was once again
organized by Mike Preuss (TU Dortmund) and Tobias Mahlmann (ITU Copenhagen),
adding Antonio Mora Garc{\'i}a from the Universidad de Granada as
third team member. Whereas the rules and even the participants
to this competition were almost identical to the AIIDE 2013
competition setup, several technical changes were made in comparison
to 2012\footnote{\url{http://ls11-www.cs.tu-dortmund.de/rts-competition/StarCraft-cig2013}}.
A new competition software was implemented by Tobias but
not completely finished in time, so that the read/write function
that enables learning between games had to be disabled again. 
This is probably the most important difference to the AIIDE competition,
however, as the result provided in table~\ref{tab:cig2013} shows, the effect is
limited. Due to the late availability of the competition software,
only 32 rounds of random robin were played, making 896 games
altogether, and 224 games by each of the 8 submitted bots.

As the map set has also been changed to the 10 standard
maps used by the AIIDE competition (without letting the competitors
know about this in advance as usual for the CIG competitions), 
the competitions were otherwise very similar. We presume that 
disabling the learning was a disadvantage for the UAlbertaBot who
won the AIIDE competition and was only runner-up to the Skynet bot
here. The 3rd place went to AIUR as in 2012, followed by 
Xelnaga and Adjutant. A direct comparison to the results of
CIG 2012 (table~\ref{tab:cig2012}) shows that bot evolution 
between these two competitions was obviously limited. It also
shows that some bots as the UAlbertaBot make good use of 
online learning, whereas others, as Skynet, do not profit from
it that much.
